\documentclass[11pt]{article}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{fontspec}
\setmainfont{Fira Sans} % Using a standard, widely available font
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\raggedright
\pagestyle{empty}

\titleformat{\section}{\bfseries\Large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=7pt}

\begin{document}

\centerline{\Huge Chris Goetz}
\vspace{5pt}
\centerline{\href{tel:409.247.4746}{409.247.4746} | \href{mailto:hire.me@chrisgoetz.com}{hire.me@chrisgoetz.com} | \href{https://www.chrisgoetz.com}{chrisgoetz.com} | \href{https://linkedin.com/in/chrisgoetz}{linkedin.com/in/chrisgoetz} | \href{https://github.com/christopherg}{github.com/christopherg}}
\vspace{-10pt}

\section*{Summary}
I am a Principal Cloud Engineer at AWS with a proven track record of solving complex technical problems, influencing product strategy, and driving industry-leading customer outcomes. My expertise lies in designing and implementing robust, scalable, and cost-effective cloud solutions for global-scale environments. I thrive on deconstructing ambiguous challenges and architecting elegant solutions that push the boundaries of technology while delivering tangible business value.

\vspace{-6.5pt}

\section*{Skills}
\textbf{Cloud Computing:} AWS (EC2, EBS, S3, IAM, RDS, VPC, CloudFormation, Lambda, ELB, Route 53), GCP \\
\textbf{Infrastructure as Code:} Terraform, CloudFormation, Ansible, CDK \\
\textbf{Programming \& Scripting:} Python, Bash, Java, PowerShell, PHP, Perl \\
\textbf{Containers \& Orchestration:} Docker, ECS, EKS \\
\textbf{Observability:} CloudWatch, Grafana, Prometheus, ELK Stack, PRTG, Splunk, New Relic, Wireshark \\
\textbf{Databases:} PostgreSQL, MySQL, DynamoDB, MS SQL, SQLite \\
\textbf{Networking:} VPN, BGP, DNS, Load Balancing, HAProxy \\
\textbf{Security:} IAM Policies, KMS, Encryption, Compliance Best Practices \\
\textbf{DevOps:} CI/CD, Jenkins, Blue-Green Deployments, Rollback Strategies \\
\textbf{Operating Systems:} Linux (RHEL, Solaris), Unix, AIX, Windows Server \\
\textbf{Virtualization:} VMware, KVM, XEN, Hyper-V

\vspace{-6.5pt}

\section*{Experience}
{\large\textbf{Principal Cloud Support Engineer,}} {Amazon Web Services (AWS)} -- REMOTE \hfill 2024 -- Present \\
\vspace{-9pt}
\begin{itemize}
    \item Lead resolution of highly ambiguous technical issues spanning multiple AWS services, often with no clear owner.
    \item Architect and execute strategic technical initiatives by providing critical industry context to senior leadership, directly influencing product roadmaps and long-term technology decisions to enhance customer success and mitigate business risk.
    \item Drive support strategy for high-profile customers, delivering guidance during critical escalations and influencing AWS service teams to remove customer pain points.
    \item Influence long-term roadmap and feature direction of AWS services through engagement with service team leadership.
    \item Lead the resolution of mission-critical, significantly complex, and often undefined technical escalations for AWS's largest clients, deconstructing ambiguous problems into actionable solutions to ensure service robustness, stability, and scalability.
    \item Design and implement scalable support frameworks, mechanisms, and operational best practices across the organization, eliminating systemic bottlenecks and enabling a force-multiplier effect on global support teams.
    \item Spearhead the professional development of the global engineering community by mentoring senior engineers, performing Principal-level promotion assessments, and disseminating knowledge on emerging technology trends and operational best practices.
    \item Drive the diagnosis and resolution of endemic, multi-system technical issues, architecting exemplary solutions that balance cost-effectiveness, architectural complexity, and long-term customer value.
    \item Create, launch, and evangelize tooling and operational processes to streamline repetitive efforts and scale support operations.
    \item Represent AWS Support in customer briefings, large-scale events, and executive-level escalations.
\end{itemize}

{\large\textbf{Senior Cloud Support Engineer,}} {Amazon Web Services (AWS)} -- REMOTE \hfill 2021 -- 2024 \\
\vspace{-9pt}
\begin{itemize}
    \item Led the end-to-end design and delivery of simplified solutions in complex technical spaces, working with a high degree of autonomy.
    \item Drove the resolution of complex business and technology problems, clearing blockers and escalating when appropriate to ensure timely delivery.
    \item Mentored and developed junior engineers, improving their skills, knowledge, and ability to get things done.
    \item Simplified and drove the use of best practices and operational excellence procedures, identifying and optimizing processes to improve team efficiency.
    \item Influenced and force-multiplied by dividing large problems into sub-problems that could be worked in parallel by multiple engineers.
\end{itemize}

{\large\textbf{Cloud Support Engineer,}} {Amazon Web Services (AWS)} -- REMOTE \hfill 2013 -- 2021 \\
\vspace{-9pt}
\begin{itemize}
    \item Provided high-quality technical support for a wide range of AWS services, including EC2, S3, VPC, and RDS, for enterprise-level customers.
    \item Drove customer communication during critical events, and applied advanced troubleshooting techniques to provide unique solutions.
    \item Worked independently to handle enterprise cases of all severities, assessing customer technical practices and recommending methods for effective service operations.
    \item Became a Subject Matter Expert (SME) in one or more services, handling escalations and reviewing cases related to my area of expertise.
    \item Created effective public content, including knowledge-base articles, how-to videos, and technical articles for the AWS customer community.
\end{itemize}

{\large\textbf{UNIX/Linux Administrator, Sr Consultant,}} {Allstate Insurance} -- Northbrook, IL \hfill 2012 -- 2013 \\
\vspace{-9pt}
\begin{itemize}
    \item Managed the lifecycle of over 3,500 Red Hat Enterprise Linux and Solaris systems, including patching, software installation, and troubleshooting.
    \item Developed and maintained complex shell, Perl, and Python scripts to automate server infrastructure.
    \item Collaborated with a geographically dispersed team in a “follow the sun” workflow to optimize infrastructure and minimize downtime.
\end{itemize}

{\large\textbf{Gaming Systems Linux/Unix Engineer,}} {Kewadin Casinos} -- Sault Ste. Marie, MI \hfill 2005 -- 2012 \\
\vspace{-9pt}
\begin{itemize}
    \item Provided 24x7 operational coverage for a complex network of AIX, Red Hat Enterprise Linux, and other mixed Linux distributions.
    \item Maintained the LAN, including daily monitoring for system failures, data backups, performance tracking, and hardware/software upgrades.
    \item Supported multiple operating systems and virtualization technologies, including Linux, UNIX, AIX, AS/400, Windows, Mac OS, Hyper-V, VMware ESX, and KVM.
\end{itemize}

\vspace{-18.5pt}

\section*{Projects}
{\large\textbf{VoIP \& Messaging Communications Platform}} \\
\vspace{-9pt}
\begin{itemize}
  \item Designed and deployed a highly available, event-driven messaging platform integrating Twilio, VoIP.ms, and DIDWW. Built on AWS Lambda, SQS, and API Gateway, the solution supports SMS, MMS, and voice with retry logic, billing via Stripe, and full JWT-based authentication.
\end{itemize}

{\large\textbf{Self-Hosted Infrastructure Automation}} \\
\vspace{-9pt}
\begin{itemize}
  \item Automated deployments for WireGuard VPN, Pi-hole DNS filtering, and Authentik SSO using Docker Compose and Terraform across hybrid environments (GCP, AWS, local). Includes CI/CD workflows for configuration updates and a storage cluster (JBOD) using software RAID (mdadm), SMART monitoring, and email alerting.
\end{itemize}

\vspace{-18.5pt}

\section*{Certifications}
\begin{itemize}
    \item AWS Certified Solutions Architect -- Professional
    \item AWS Certified DevOps Engineer -- Professional
    \item AWS Certified SysOps Administrator
    \item ITIL Foundations v3
\end{itemize}

\vspace{-18.5pt}

\section*{Education}
{\large\textbf{Lake Superior State University}} -- Sault Sainte Marie, MI \hfill 2008 -- 2012 \\
Bachelor of Science in Computer Networking, Associate of Science in Computer Science

\end{document}
